SDR enhancement by clouds

### 2024-03-27 article/article.tex
Commit 2024-03-27 12:12

The shortwave solar irradiance, reaches the Earth's surface, is the main energy
source of the planet. It drives and governs the climate.
It has direct practical application, in different energy production method.
\ldots. cite \ldots.
The variability of its intensity, can cause difficulties in predicting the yield and
designing the appropriate equipment.
\ldots. cite \ldots.
An aspect of this variability are the interaction with the clouds, where locally, under some
conditions the total shortwave irradiance reaching the ground can be higher than the
expected clear sky irradiance.
\ldots. cite \ldots.
Those enhancements have been reported to be able to exceed \ldots. and duration.
\ldots. cite \ldots.

There are some propositions of the underling mechanism of those events as summarized
by Gueymard (2017), and include scattering on the edge of cumulus clouds or through
thin cirrus. Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing explanation, the forward Mie scattering
(Pecenak et al. 2016; Thuillier et al. 2013; G. H. Yordanov et al. 2013; Georgi Hristov Yordanov, Saetre, and Midtgård 2015).
The overall phenomenon depends on different interactive factors, that include cloud
thickness and constitution, and the relative position of the sun, the clouds and the
observer. As such, there can be multiple contributing mechanism that create the
observed enhancements.

@@

Gueymard, 2017; Veerman et al., 2022)
Methods of identification in the literature include the use of a clear sky radiation
modelel

@@

@@

@@

>>>>

The shortwave solar irradiance, reaches the Earth's surface, is the main energy
source of the planet. It drives and governs the climate.
It has direct practical application, in different energy production method.
\ldots. cite \ldots.
The variability of its intensity, can cause difficulties in predicting the yield and
designing the appropriate equipment.
\ldots. cite \ldots.
A big aspect of this variability are the interaction with the clouds. In general
clouds, absorb part of the solar irradiance, but under certain conditions, can
enhance the total shortwave irradiance reaching the ground. This effect can locally
increase the observed total shortwave irradiance higher than the expected clear sky
irradiance {[}see references therein{]}.
\ldots. cite \ldots.
Those enhancements have been reported to be able to exceed \ldots. and duration.
\ldots. cite \ldots.
Martins, Mantelli, and Rüther (2022)

Some of the proposed underling mechanisms of those events have been summarized
by Gueymard (2017), and include scattering on the edge of cumulus clouds or through
thin cirrus. Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing mechanism, the forward Mie scattering
(Pecenak et al. 2016; Thuillier et al. 2013; G. H. Yordanov et al. 2013; Georgi Hristov Yordanov, Saetre, and Midtgård 2015), through the clouds.
The overall phenomenon depends on different interactive factors, that include cloud
thickness and constitution, and the relative position of the sun, the clouds, and the
observer. As such, there multiple contributing mechanism can create the
observed irradiance enhancements.

@@

It has been reported than enhancements events can interfere in the comparison of
ground data and satellite observe ovations (Damiani et al. 2018)

Instruments respose \ldots.
Martins, Mantelli, and Rüther (2022)

Study of the mechanism has also been done with modeling of different cloud types and
atmospheric conditions.
Gueymard (2017); Veerman, Van Stratum, and Van Heerwaarden (2022)

Methods of identification in the literature usually include the use of a simulated clear sky radiation
Vamvakas, Salamalikis, and Kazantzidis (2020); Mol, Knap, and Van Heerwaarden (2023);

@@

\leavevmode\vadjust pre{\hypertarget{ref-Damiani2018}{}}%
Damiani, Alessandro, Hitoshi Irie, Takashi Horio, Tamio Takamura, Pradeep Khatri, Hideaki Takenaka, Takashi Nagao, Takashi Y. Nakajima, and Raul R. Cordero. 2018. {``Evaluation of Himawari-8 Surface Downwelling Solar Radiation by Ground-Based Measurements.''} \emph{Atmos. Meas. Tech.}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Martins2022}{}}%
Martins, G. L., S. L. Mantelli, and R. Rüther. 2022. {``Evaluating the Performance of Radiometers for Solar Overirradiance Events.''} \emph{Solar Energy} 231 (January): 47--56. \url{https://doi.org/10.1016/j.solener.2021.11.050}.

\leavevmode\vadjust pre{\hypertarget{ref-Mol2023}{}}%
Mol, Wouter B., Wouter H. Knap, and Chiel C. Van Heerwaarden. 2023. {``Ten Years of 1 Hz Solar Irradiance Observations at Cabauw, the Netherlands, with Cloud Observations, Variability Classifications, and Statistics.''} \emph{Earth System Science Data} 15 (5): 2139--51. \url{https://doi.org/10.5194/essd-15-2139-2023}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Veerman2022}{}}%
Veerman, M. A., B. J. H. Van Stratum, and C. C. Van Heerwaarden. 2022. {``A Case Study of Cumulus Convection over Land in Cloud‐resolving Simulations with a Coupled Ray Tracer.''} \emph{Geophysical Research Letters} 49 (23). \url{https://doi.org/10.1029/2022GL100808}.
